\section{Overlays}
\label{sec:overlays}

This chapter describes all the available screens.
For easy positioning of the overlays, an overlay can have the optional property \texttt{position} which controls the position of the overlay on the screen.

\subsection{Current Time}
\label{sec:overlays-current-time}
This overlay just displays the current time with hours, minutes and seconds.

\subsection{Screen Freeze}
\label{sec:overlays-screen-freeze}
The screen freeze overlay will block all user input for a configurable amount of time to induce more stress.
The freeze will start after a configurable amount of time.
The timer will run as soon as the first screen has started and does not take into account how long a user may wait until he clicks the next button on the \nameref{sec:screens-start} or \nameref{sec:screens-message} screen.
Therefore it can not be controlled on which screen the freeze happens if a screen with a next button is in the stress test.

\subsection{Webcam}
\label{sec:overlays-webcam}
The Webcam overlay will display the live recordings of the user's webcam on the screen.
To be able to access the webcam the user must give the Stress+ website the permission to do so.
Some operating systems might also restrict access to the webcam.
It is also generally not possible that two programs access the webcam simultaneously.
If the webcam can not be accessed, the stress test will continue without displaying the live recordings of the webcam.

\subsection{Chatbot}
\label{sec:overlays-chatbot}
This is an overlay version of the \nameref{sec:screens-chatbot} screen, that can be opened and closed via button.
For further details consult the \nameref{sec:screens-chatbot} screen documentation.


\subsection{Heartbeat}
\label{sec:overlays-heartbeat}
This overlay will display the heart rate next to a heart image with a bumping animation.
The heartrate is completely faked and will slightly increase over time.
This overlay can be displayed delayed by specifying a duration in seconds after which it will become visible.
