\section{Screens}
\label{sec:screens}

This chapter describes all available screens.

\subsection{Math test}
\label{sec:screens-math-test}

\begin{table}[ht]
  \begin{tabularx}{\textwidth}{l|l|X}
    Property & Type & Description \\
    \hline
    \texttt{answerTimeout} & \texttt{number} & The duration in seconds for answering one math question \\
    \texttt{waitTime} & \texttt{number} & The duration inseconds between two math questions \\
    \texttt{testTotalTime} & \texttt{number} & The total duration of the math test \\
    \texttt{enableSound} & \texttt{boolean} & Play an anyoing sound during the math test \\
    \texttt{enableControl} & \texttt{boolean} & Enable control mode \\
    \texttt{difficulty} & \texttt{number} & The initial difficulty of the math questions (Easy: $0$; Hard: $4$) \\
  \end{tabularx}
  \caption{Properties of the Math test screen}
\end{table}

\subsection{Message}
\label{sec:screens-message}
The Message screen shows a simple message to the user.
The user can go to the next screen by clicking a button on the screen.
The title, the message and the button text of this screen can be adjusted.

\subsection{Wait Screen}
\label{sec:screens-wait-screen}

The Wait screen shows a simple message to the user, like the \nameref{sec:screens-message} screen.
But the user has to wait a specific time until the next screen is displayed.
The user can not manually go to the next screen.
The title, the message and the timeout in seconds of this screen can be adjusted.

\subsection{Chatbot}
\label{sec:screens-chatbot}

\subsection{Start}
\label{sec:screens-start}

This screen can be used as the first screen.
It displayes the Stress+ logo and can show a custom message.

\subsection{End}
\label{sec:screens-end}

This screen can be used as the last screen.
It displayes the Stress+ logo and can show a custom message.

Note: The end screen has no mechanism to go the next screen if it is placed in the middle of the pipeline.
If the end screen is not present a blank page will be shown as last screen.

\subsection{Survey}
\label{sec:screens-survey}

The survey screen can display other websites inside the stress test. 
This can be usefull to display Google Forms inside a stress test.
A button will always be displayed on the top of the screen to navigate to the next screen.
